Trends of SDR in Thessaloniki

### 2023-07-15 Article.Rmd
Commit 2023-07-15 22:14

<!-- cost fuction -->
\begin{equation}
f(a)=\frac{1}{n}\sum_{i=1}^{n}( \text{SDR}_{\text{CSid},i} - a \times \text{SDR}_{\text{testCSref},i})^2 \label{eq:minf}
\end{equation}

@@

>>>>

<!-- cost fuction -->
\begin{equation}
f(a) = \frac{1}{n}\sum_{i=1}^{n} ( \text{SDR}_{\text{CSid},i} - a \times \text{SDR}_{\text{testCSref},i} )^2 \label{eq:minf}
\end{equation}

where: $n$ is the total number of daylight records, $\text{SDR}_{\text{CSid},i}$ are the records identified as clear sky by CSid, $a$ is a hypothetical adjustment factor, and $\text{SDR}_{\text{testCSref},i}$ is the tested model clear sky radiation.

@@

where: $\text{SDR}_\text{CSref}$ is the reference clear sky SDR, in $w\;m^{-2}$.
